---
title: "RWeekly Curinator Processing Report"
author: "RWeekly Team"
date: "`r Sys.Date()`"
format: 
  html:
    toc: true
    toc-depth: 2
    theme: bootstrap
    embed-resources: true
    code-fold: true
    code-summary: "Show code"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE,
  fig.width = 8,
  fig.height = 6
)
```

## Overview

This report processes the latest curinator content using AI to categorize and filter R-related posts for RWeekly curation.

## Load Required Libraries

```{r libraries}
library(dplyr)
library(ellmer)
library(ragnar)
library(purrr)
library(reticulate)
library(jsonlite)
library(tidyr)
library(glue)
library(knitr)
library(DT)

source("parse_curinator.R")
```

## Helper Functions

```{r helper-functions}
read_md <- function(filepath) {
  paste(readLines(filepath), collapse = "\n")
}

try_read_as_markdown <- function(url){
  tryCatch(
    ragnar::read_as_markdown(url),
    error = function(e) {
      warning("Failed to read URL: ", url, " - ", e$message)
      NA  # Return NA when there's an error
    }
  )
}
```

## Data Processing

### Step 1: Parse Curinator Content

```{r parse-curinator}
md_links <- parse_curinator_md("../curatinator_latest.md") |>
  filter(`type` == "RSS POSTS") |>
  mutate(content = map_chr(link, try_read_as_markdown)) |>
  # limit character length of content to 1500 characters to respect model token limits
  mutate(content = substr(content, 1, 1500))

cat("📊 **Total links processed:**", nrow(md_links), "\n")
cat("📋 **Links with content:**", sum(!is.na(md_links$content)), "\n")
cat("❌ **Links without content:**", sum(is.na(md_links$content)), "\n")
```

### Step 2: AI Processing Setup

```{r ai-setup}
system_prompt <- read_md("curinator_system_prompt.md")

chat <- chat_anthropic(
  system_prompt = system_prompt,
  model = "claude-opus-4-1-20250805"
)

set.seed(as.numeric(Sys.time()))
xml_tag <- paste0("info_", sample(500:9999, 1))

prompts <- interpolate(
  "<{{xml_tag}}>
  Title: {{md_links$title}}
  Link: {{md_links$link}}
  Content: {{md_links$content}}
  </{{xml_tag}}>"
)
```

### Step 3: AI Analysis

```{r ai-analysis}
cat("🤖 **Processing links with AI...**\n")

result_raw <- md_links |>
  mutate(
    json_metadata = parallel_chat_text(
      chat,
      prompt = prompts
    )
  )

cat("✅ **AI analysis complete!**\n")
```

### Step 4: Parse AI Results

```{r parse-results}
result_temp <- result_raw |>
  mutate(metadata = map(json_metadata, ~ fromJSON(gsub("```(json\n)*", "", .x)))) |>
  unnest_wider(metadata)

cat("📈 **Results summary:**\n")
if("is_r_related" %in% names(result_temp)) {
  cat("   - R-related posts:", sum(result_temp$is_r_related == "yes", na.rm = TRUE), "\n")
  cat("   - Non R-related posts:", sum(result_temp$is_r_related != "yes", na.rm = TRUE), "\n")
  cat("   - Unclear classification:", sum(is.na(result_temp$is_r_related)), "\n")
}
```

---

## 📋 **FINAL REPORT FOR CURATORS**

### ✅ R-Related Content (Ready for Publication)

```{r r-related-content, results='asis'}
result_wrangled <- result_temp |>
  filter(is_r_related == "yes") |>
  mutate(md_link = glue("[{title}]({link})")) |>
  group_by(category) |>
  summarise(
    combined_text = paste(md_link, collapse = '\n'),
    count = n(),
    .groups = "drop"
  ) |>
  arrange(desc(count))

if(nrow(result_wrangled) > 0) {
  for(i in 1:nrow(result_wrangled)) {
    cat("\n#### ", result_wrangled$category[i], " (", result_wrangled$count[i], " items)\n\n")
    # Split the combined text and add each link on a new line
    links <- strsplit(result_wrangled$combined_text[i], "\n")[[1]]
    for(link in links) {
      cat(link, "\n\n")
    }
  }
} else {
  cat("*No R-related content found.*\n")
}
```

### 🔍 Manual Review Required

```{r manual-review, results='asis'}
manual_review_links <- result_temp |>
  filter(is.na(content)) |>
  mutate(md_link = glue("[{title}]({link})")) |>
  pull(md_link)

if(length(manual_review_links) > 0) {
  cat("The following links could not be automatically processed and require manual review:\n\n")
  for(link in manual_review_links) {
    cat(link, "\n\n")
  }
} else {
  cat("*No links require manual review.*")
}
```

### ❌ Flagged as Not R-Related

```{r not-r-related, results='asis'}
flagged_not_r_related <- result_temp |>
  filter(is_r_related != "yes" & !is.na(is_r_related)) |>
  mutate(md_link = glue("[{title}]({link})")) |>
  pull(md_link)

if(length(flagged_not_r_related) > 0) {
  cat("The following links were flagged as not R-related:\n\n")
  for(link in flagged_not_r_related) {
    cat(link, "\n\n")
  }
} else {
  cat("*No links were flagged as not R-related.*")
}
```

---

## 📊 **Detailed Analysis Tables**

### Processing Summary

```{r summary-table}
summary_data <- data.frame(
  Metric = c(
    "Total Links Processed",
    "Links with Content",
    "Links without Content",
    "R-Related Posts",
    "Non R-Related Posts",
    "Manual Review Required"
  ),
  Count = c(
    nrow(md_links),
    sum(!is.na(md_links$content)),
    sum(is.na(md_links$content)),
    sum(result_temp$is_r_related == "yes", na.rm = TRUE),
    sum(result_temp$is_r_related != "yes" & !is.na(result_temp$is_r_related), na.rm = TRUE),
    sum(is.na(result_temp$content))
  )
)

kable(summary_data, caption = "Processing Summary")
```

### R-Related Content by Category

```{r category-table}
if("category" %in% names(result_temp) && sum(result_temp$is_r_related == "yes", na.rm = TRUE) > 0) {
  category_summary <- result_temp |>
    filter(is_r_related == "yes") |>
    count(category, sort = TRUE) |>
    rename(Category = category, Count = n)
  
  DT::datatable(category_summary, 
                caption = "R-Related Content by Category",
                options = list(pageLength = 10))
} else {
  cat("*No R-related content to categorize.*")
}
```

### All Processed Links

```{r all-links-table}
display_data <- result_temp |>
  select(title, link, is_r_related, category) |>
  mutate(
    title = substr(title, 1, 50),  # Truncate long titles
    link = paste0('<a href="', link, '" target="_blank">Link</a>')
  )

DT::datatable(display_data, 
              escape = FALSE,
              caption = "All Processed Links",
              options = list(
                pageLength = 10,
                scrollX = TRUE
              ))
```

---

## 📝 **Notes for Curators**

- **Green sections** (R-Related Content) are ready for publication in RWeekly
- **Yellow sections** (Manual Review) need human verification
- **Red sections** (Not R-Related) have been filtered out by AI but should be double-checked
- Use the interactive tables below for detailed analysis
- All links open in new tabs when clicked

**Report generated on:** `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`